
\section{Conclusion}
In order to get a close to reality simulation, it was necessary during the course of this thesis, to find a solution that wouldn't be limited to simulating isolated aspects of the problem, but all the complete set of functionalities that would allow to solve the problem.

A big part of this problem was solved by finding MiXiM, but the lack of a good routing protocol available in it and node tracking system, made it clear that it was necessary to find and implement modules that would solve this limitation.

This thesis allowed the development of a fully integrated system, called EMoS, with the objective of tracking people inside a house, specially dedicated to elder people.

The large quantity of references made in this thesis made it impossible to fully achieve an intelligent system that would specially track an elder person. Nevertheless a base simulation where other modules can be built on top was completed and the problematic of tracking analysed and understood.

In the future a better solution for the tracking system can be found, removing the need for an offline process, which would be very time consuming in real conditions.

Another possibility is the implementation in the node of a parallel stack of layers that would allow the same node to communicate with a bluetooth network, extending the simulation to a BSN simulation with biologic events like heartbeat or blood pressure.

The improvement of the obstacles model could also be achieved in order to get better and close to real simulation parameters.

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

%\appendices
%\section{Proof of the First Zonklar Equation}
%Appendix one text goes here.

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
%\section{}
%Appendix two text goes here.